Lexical frequency mediates the facilitation effect of cognateness in bilingual lexical acquisition

### 2023-03-29 manuscript/appendix/_model-predictors.qmd
New version of the manuscript, with revised Discussion

## Word exposure index

@@

We created a predictor ($Exposure$) to account for the exposure rate of each child to each of the words their parents responded to, weighted by the child's exposure to the language the word belongs to. the exposure of the $i$-th child to the $j$-th word measure is the product of the lexical frequency of the word (Zipf score) and the child’s degree of exposure to the corresponding language (a proportion) (see @eq-exposure).

$$
\textbf{Exposure}_{ij} = \textbf{Frequency}_i \times \textbf{DoE}_{j}
$$ {#eq-exposure}

@@

## Levenshtein similarity

>>>>

## Word exposure index  {.unnumbered}

@@

We created a predictor ($\text{Exposure}$) to account for the exposure rate of each child to each of the words their parents responded to, weighted by the child's exposure to the language the word belongs to. the exposure of the $i$-th child to the $j$-th word measure is the product of the lexical frequency of the word (Zipf score) and the child’s degree of exposure to the corresponding language (a proportion) (see @eq-exposure).

$$
\text{Exposure}_{ij} = \text{Frequency}_i \times \text{DoE}_{j}
$$ {#eq-exposure}

@@

## Levenshtein similarity {.unnumbered}
